Master thesis

### 2017-07-24 02-Introduction.Rmd
Final soutenance 2

>>>>

In the present study, we focused on mechanisms involved in the relationship between biodiversity and forest ecosystem resilience. We used a simulation approach using TROLL model to assess long term processes for different types and levels of disturbances. We first assessed diversity effect on forest resilience of structure and functionning using numerous indices of taxonomic and functional diversities. Then, we measured biodiversity net effect, partitioned into complementarity and selection effects, resilience for several ecosystem metrics.
